### 2020-08-11 manuscript/manuscript.rmd
add CAT60, and CAT270 results in Fig. 4

Philippe2009$model =
  factor(
    Philippe2009$model,
    levels = c("Poisson+CAT270", "Poisson+CAT360", "Poisson+CAT400", "Poisson+CAT440", "Poisson+CAT480"))

@@

p3 = Whelan2017_full_only_choanozoa %>%
  ggplot( aes(model)) +
  geom_line(aes(y = `support_ctenophora_sister`, colour = "Ctenophora-sister", group = 1), color = ("#E69F00")) +
  geom_point(aes(y = `support_ctenophora_sister` ), color = ("#E69F00")) +
  geom_line(aes(y = `support_porifera_sister`, colour = "Porifera-sister", group = 1), color = ("#009E73")) +
  geom_point(aes(y = `support_porifera_sister` ), color = ("#009E73")) +
  scale_fill_manual(values = c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Number of CAT substitutional categories", y = "Support") +
  ggtitle("Whelan2017_full_Choanozoa")

@@

ggarrange(p1, p2, p3, p4,  ncol  = 2, nrow = 2, labels = c("A", "B", "C", "D"))

>>>>

Philippe2009$model =
  factor(
    Philippe2009$model,
    levels = c("Poisson+CAT60", "Poisson+CAT270", "Poisson+CAT360", "Poisson+CAT400", "Poisson+CAT440", "Poisson+CAT480"))

@@

p3 = Whelan2017_full_only_choanozoa %>%
  ggplot( aes(model)) +
  geom_line(aes(y = `support_ctenophora_sister`, colour = "Ctenophora-sister", group = 1), color = ("#E69F00")) +
  geom_point(aes(y = `support_ctenophora_sister` ), color = ("#E69F00")) +
  geom_line(aes(y = `support_porifera_sister`, colour = "Porifera-sister", group = 1), color = ("#009E73")) +
  geom_point(aes(y = `support_porifera_sister` ), color = ("#009E73")) +
  scale_fill_manual(values = c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Number of CAT substitutional categories", y = "Support") +
  ggtitle("Whelan2017_full_Choanimalia")

@@

ggarrange(p1, p2, p3, p4,  ncol  = 2, nrow = 2, labels = c("A", "B", "C", "D"), common.legend = TRUE)
